### 2020-01-04 methods.tex
latest PDF
pre-Activation Maps

We assume we are given several pretrained Deep Neural Networks (DNNs), as part of a similar architecture.
We would like to estimate the trends in the reported test / generalization accuracy accross a series of similar archtectures.  
For example, below we compare the 8 pretrained models in the VGG series: (VGG11, VGG11\_BN$\cdots$ VGG19), with
and without Batch Normalization, trained on ImageNet, and widely available in the pyTorch distribution.

To do this, we will compute a variety of \emph{Complexity Metrics} based on the Product Norm of the layer weight matrics.
Note that unlike traditional ML approaches, however, we do not seek a bound on the complexity (i.e. test error), 
nor are we trying to evaluating a single model with differing hyperparmeters.  We wish to examine different models a 
common architecture series. And, also, compare different architectures themselves.

@@

\charles{not actually feature Maps, need to find the correct term: Tensor Slice}

\paragraph{Spectral Analysis of Convolutional 2D Layers}
While we can easily analyze Linear layers, there is some ambiguity in performing spectral analysis on Convolutional 2D (Conv2D) layers.  A Conv2D layer is a 4-index tensor of dimension $(w,h,in\_ch,out\_ch)$, specified by an $(w\times h)$ filter, and $in\_ch,out\_ch$ input and output channels, respectively.  Typically, the $w=h=k$,  giving $(k\times k)$ Tensor Slices $\mathbf{W}_{i,L}$
of dimension $(in\_ch\times out\_ch)$ each.  Usually $in\_ch\ll out\_ch$.
There are at least 3 different approaches to computing the Singular Values Decomposition(s) (SVD) of an Conv2D layer
\begin{enumerate}
\item run SVD on each of the Tensor Slices $\mathbf{W}_{i,L}$, yielding $(k\times k)$ sets of $M$ singular values. 
\item stack the feature maps into a single rectangular matrix of, say, dimension $((k\times k\times out\_ch)\times in\_ch)$, yielding $in\_ch$ singular values
\item Compute the 2D Fourier Transform (FFT) for each of the $(in\_ch, out\_ch)$ pairs, and run SVD on the resulting Fourier coeffients\cite{Long2019}.  This leads to $\sim(k\times in\_ch\times out\_ch)$ non-zero singular values.
\end{enumerate}

>>>>

We assume we are given several pretrained Deep Neural Networks (DNNs), as part of a similar architecture.
We would like to estimate the trends in the reported test / generalization accuracy accross a series of similar archtectures.  
and without Batch Normalization, trained on ImageNet, and widely available in the pyTorch distribution.

\paragraph{Empirical Complexity Metrics}
To do this, we will compute a variety of \emph{Complexity Metrics} based on the Product Norm of the layer weight matrics.
Note that unlike traditional ML approaches, however, we do not seek a bound on the complexity (i.e. test error), 
nor are we trying to evaluating a single model with differing hyperparmeters.  We wish to examine different models a 
common architecture series. And, also, compare different architectures themselves.

@@

\paragraph{Spectral Analysis of Convolutional 2D Layers}
While we can easily analyze Linear layers, there is some ambiguity in performing spectral analysis on Convolutional 2D (Conv2D) layers.  A Conv2D layer is a 4-index tensor of dimension $(w,h,in\_ch,out\_ch)$, specified by an $(w\times h)$ filter (or kernel), and $in\_ch,out\_ch$ input and output channels, respectively.  Typically, the $w=h=k$,  giving $(k\times k)$ tensor slices, or \emph{pre-Activation Maps} $\mathbf{W}_{i,L}$ of dimension $(in\_ch\times out\_ch)$ each.  Usually $in\_ch\le out\_ch$.

There are at least 3 different approaches to computing the Singular Values Decomposition(s) (SVD) of an Conv2D layer
\begin{enumerate}
\item run SVD on each of the pre-Activation Maps $\mathbf{W}_{i,L}$, yielding $(k\times k)$ sets of $M$ singular values. 
\item stack the feature maps into a single rectangular matrix of, say, dimension $((k\times k\times out\_ch)\times in\_ch)$, yielding $in\_ch$ singular values
\item Compute the 2D Fourier Transform (FFT) for each of the $(in\_ch, out\_ch)$ pairs, and run SVD on the resulting Fourier coeffients\cite{Long2019}.  This leads to $\sim(k\times in\_ch\times out\_ch)$ non-zero singular values.
\end{enumerate}
